More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-02-13 2016-Weak-FH-Bisim/WeakBisim.tex
revue des preuves

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1})\land\Pred\,^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land (\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})\\
\Post={x^3_{mk}\gets (e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})^{k\in K_m}}
$

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact
the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (\WTDeux) we directly conclude 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively). \LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
\begin{mathpar}
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
\end{mathpar}

By recurrence hypothesis the theorem is \True~ for any set of transitions of length $l$. In particular, we have

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \implies  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
}
\end{mathpar}

We need to prove the same implication with  by adding the transition:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}
It will remain so. First by using rule (\WTDeux) we can directly conclude :
\begin{mathpar}

 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
\implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

On the other hand, by rule (\WTUn) we have
\begin{mathpar}
 \openrule
         {
          \emptyset,\True,\Id(s')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\end{mathpar}

Finally by using rule (\WTTrois) we compose the three weak transitions:

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \vis{\set{\beta}},\Pred,\Post   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\qquad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
          \vis{\set{\beta}} \dotcup \set{\gamma},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s''} \in\WT
} \WTTrois
\end{mathpar}

The right part of the disjunction, i.e.
\begin{mathpar}
\Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
\end{mathpar}
is handled trivially by rule (\WTUn)

\end{itemize}

\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition.

\begin{itemize}
\item Case rule (\WTUn):
\begin{mathpar}
{\openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}\! \implies\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
\end{mathpar}

\item Case rule (\WTDeux):
\begin{mathpar}
\openrule
         {
           \set{\gamma},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'} \in \WT \implies
         \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'} \in \mathcal{T}         
\end{mathpar}
where $\set{\gamma} = \vis{\set{\beta}}$.
These two cases prove the implication with $n=0$ and $m=0$.

\item Case rule (\WTTrois):
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

\item Similarly, a series of $m_1=n+m+1$  open transitions can be simplified: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \set{\beta^2_i},\Pred^2_i,\Post^2_i   }
         {s^2_i \OTarrow {\tau} s^2_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where\\
$
s_2=s^2_0 \wedge s^2_{m_1}=s',
\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^2_i}}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^2_i,\Post_2\!=\! \biguplus_{i=0}^{m_1} \Post_i^2\\
$

\item Concerning the middle reduction, by induction hypothesis there exist a set of transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\bigg(\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta^4},\Pred^4,\Post^4 }
         {s^4 \OTarrow {\alpha} s'^4} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \set{\beta^5_i},\Pred^5_i,({x^5_k\gets e^5_k})^{k\in K}    }
         {s^5_i \OTarrow {\tau} s^5_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
$
s_1=s^3_0 \wedge s^3_{n_2}=s^4 \wedge s'^4 = s^5_0 \wedge s^5_{m_2}=s_2,
\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta^3_i}} \dotcup  \vis{\set{\beta^4}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^5_i}}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^3_i\land\Pred\,^4\bigotimes_{i=0}^{n_2}\subst{\Post^3_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^5_i\subst{\Post^4}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^1_i}
\\
\Post_2= ({x^5_k\gets (e^5_k\subst {\Post^4})\bigotimes_{i=0}^{n_2}\subst{\Post^3_i}})^{k\in K}
$
\end{enumerate}
~~\\
Therefore, we can deduce that:
\begin{mathpar}
\bigg( { \openrule
         {
           \set{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \set{\beta^6_i},\Pred^6_i,\Post^6_i   }
         {s^6_i \OTarrow {\tau} s^6_{i+1}} \in\mathcal{T} \wedge

\openrule
         {
           \set{\beta^7},\Pred^7,\Post^7 }
         {s^7 \OTarrow {\alpha} s'^7} \in \mathcal{T}
\wedge
\forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
         {\set{\beta^8_i},\Pred^8_i,({x^8_k\gets e^8_k})^{k\in K}    }
         {s^8_i\OTarrow {\tau} s^8_{i+1}}\in\mathcal{T}\Bigg)  
\end{mathpar}

>>>>

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land\Pred^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j}\Big)\\
\Post=\big({x^3_{mk}\gets e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j}\big)^{k\in K_m}}
$

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (\WTDeux) we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively). \LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Let us consider the sequence of ($n+m+1$) open transitions:
\begin{mathpar}
\Big(\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Big) 
\end{mathpar}

By recurrence hypothesis we suppose that the statement holds for some  set of open transitions of length $l$. In particular, we have:\\

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\, \wedge\\
~~\hspace{5.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
\Big) \\       
          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
}
$

We need to prove that   by adding the following open transition the implication remains true:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred\,',\Post\,'}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}
First by using rule (\WTDeux) we have:
\begin{mathpar}

 \openrule
         {
           \set{\beta},\Pred\,',\Post\,'}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
\implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred\,',\Post\,'
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

On the other hand, by rule (\WTUn) we can write the following weak open transition:
\begin{mathpar}
 \openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\end{mathpar}

Finally by applying rule (\WTTrois) on  the above weak open transitions:

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \vis{\set{\beta}},\Pred\,',\Post\,'   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\qquad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\\
\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
          \vis{\set{\beta}} \dotcup \set{\gamma},
		\Pred\,'',\Id(s'')
				 } 
         {s \OTWeakarrow {\alpha} s''} \in\WT
} \WTTrois
\end{mathpar}

The right part of the disjunction, i.e.,
\begin{mathpar}
\Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
\end{mathpar}
is handled trivially by rule (\WTUn). 
\end{itemize}

\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition. So we consider the different rules:

\begin{itemize}
\item Case rule (\WTUn). We have:
\begin{mathpar}
{\openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}
\end{mathpar}
We can directly conclude by the right part of the disjunction the following:\\

$
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s}\! \in\! \WT
}\!\! \implies\!\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
$
\item Case rule (\WTDeux). We have:
\begin{mathpar}
\openrule
         {
           \set{\gamma},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'} \in \WT \implies
         \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}         
\end{mathpar}
where $\set{\gamma} = \vis{\set{\beta}}$.\\

These two cases above prove the implication with $n=0$ and $m=0$.

\item Case rule (\WTTrois). We have:
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\quad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha} s''} \in \WT
\quad
\openrule
         {
           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s'' \OTWeakarrow {\tau} s'''} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'''} \in\WT
}
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\implies 
 \forall i \in [0..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1i}}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred_{1i}, \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}}\\
$
\TODO{$\Post_1= \biguplus_{i=0}^{n_1} \Post_{1i}$ or bigotimes?}
\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\implies 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where\\
$
s''\!=\!s_{30} \wedge s_{3(m_1+1)}\!=\!s''',
\displaystyle{\set{\gamma_3}\!=\!\mybigdotcup_{i=0}^{m_1}\vis{\set{\beta_{3i}}}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred_{3i},\Post_3\!=\!\bigotimes_{i=0}^{m_1} \subst{\Post_{3i}}\\
$

\item Concerning the middle reduction, by induction hypothesis there exist a set of open transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha} s''} \in\! \WT
\implies 
\bigg(\forall i \in [0..n_2].\openrule
    {
       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [0..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},({x_k\gets e_k})^{k\in K}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}
where\\
$
s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}} \dotcup  \vis{\set{\beta'}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{2i}'}}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\land\Pred\,'\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}\land \big(\bigwedge_{i=0}^{m_2}\Pred_{2i}^{\,\prime}\subst{\Post\,'}\big)\bigotimes_{i=0}^{n_1}\subst{\Post_{2i}}
\\
\Post_2= \big({x_k\gets e_k\subst {\Post\,'}\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}}\big)^{k\in K}
$
\end{enumerate}
~~\\
Therefore, we can deduce that we have:
\begin{mathpar}
{ \openrule
         {
           \set{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
 \implies
\bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\wedge\,
\forall i \in [0..(m_1\!+\!m_2)].\openrule
         {\set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\bigg)  
\end{mathpar}

such that\\
$
s_i^1= \left\{
 \begin{array}{ll}
s_{1i} & \mbox{if }i<n_1\\
s_{2i-n_1} & \mbox{if }i\geq n_1\\
\end{array}
\right. \quad \wedge \quad
s_i^3= \left\{
 \begin{array}{ll}
s_{3i} & \mbox{if }i<m_1\\
s_{2i-m_1}' & \mbox{if }i\geq m_1\\
\end{array}
\right. \\
~~\\
s\!=\!s^1_0 \wedge s^1_{(n_1+n_2+1)}\!=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{(m_1+m_2+1)}\!=\!s'''\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^1_i}}
\dotcup\vis{\set{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^3_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\bigotimes_{i=0}^{n_2}\subst{\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^1_i\subst{\Post^2}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^1_i}}
\\
\displaystyle{\Post= \big({x^3_k\gets e^3_k\subst {\Post^2}\bigotimes_{i=0}^{n_2}\subst{\Post^1_i}}\big)^{k\in K}}
$\\
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. \qed
\end{itemize}
\end{proof}
